Canonical rings of log spin stacky curves

### 2015-07-08 curves-write-up/spin_cring.tex
changed additionally

\begin{rem}
\label{rem:cusp-generation-4}
Here, we describe how to obtain a slightly better bound for our application to modular forms from example ~\ref{eg:congruence-bounds}. A careful scrutiny of Theorem ~\ref{thm:g-0-main} reveals that, if $\Delta > 0$ and $\sx$ has signature $(0;3, \ldots, 3; \delta)$, then $R_L$ is generated in weight at most 4. Since $\delta > 0$, $L_X$ is effective. Addtionally, $R_{L_X}$ is generated in weight 1, and inductive applications of Lemma ~\ref{lem:sat-1} only add generators in weights 3 and 4 and relations in weight at most 8. Therefore, $R_L$ is generated in weight at most 4 with relations in weight at most 8. Note that a similar analysis of the proof of Theorem ~\ref{thm:g-1-main} yields that when $g = 1$, congruence subgroups are generated in weight at most 4 with relations in weight at most 8.
\end{rem}

>>>>

\begin{rem}
\label{rem:cusp-generation-4}
Here, we describe how to obtain a slightly better bound for our application to modular forms from example ~\ref{eg:congruence-bounds}. A careful scrutiny of Theorem ~\ref{thm:g-0-main} reveals that, if $\Delta > 0$ and $\sx$ has signature $(0;3, \ldots, 3; \delta)$, then $R_L$ is generated in weight at most 4. Since $\delta > 0$, $L_X$ is effective. Additionally, $R_{L_X}$ is generated in weight 1, and inductive applications of Lemma ~\ref{lem:sat-1} only add generators in weights 3 and 4 and relations in weight at most 8. Therefore, $R_L$ is generated in weight at most 4 with relations in weight at most 8. Note that a similar analysis of the proof of Theorem ~\ref{thm:g-1-main} yields that when $g = 1$, congruence subgroups are generated in weight at most 4 with relations in weight at most 8.
\end{rem}
